\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.0in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}
\setlength{\footskip}{4.0pt} % Fixes the fancyhdr footskip warning

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure generated PDF is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubheadingRole}[2]{
  \vspace{4pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\begin{center}
    % Removed \scshape from here to fix the font shape undefined error
    \textbf{\Huge Yusuf Celal Zeybek} \\ \vspace{4pt}
    \small Buca, Izmir, Turkey $|$ +90 551 956 29 93 $|$ 
    \href{mailto:yusufz27x@gmail.com}{\underline{yusufz27x@gmail.com}} $|$ 
    \href{https://github.com/yusufz27x}{\underline{GitHub: yusufz27x}} $|$ 
    \href{https://www.linkedin.com/in/yusuf-celal-zeybek-5a4b92259}{\underline{LinkedIn}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Izmir Institute of Technology}{Urla, Izmir, Turkey}
      {B.Sc. in Computer Engineering (Transfer Student)}{Sept. 2023 -- Sept. 2026}
    \resumeSubheading
      {Izmir Katip Celebi University}{Cigli, Izmir, Turkey}
      {B.Sc. in Computer Engineering (GPA: 3.28)}{Sept. 2022 -- Aug. 2023}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Jotform}{Urla, Izmir, Turkey}
      {Frontend Support Engineer}{Nov. 2025 -- May 2026}
      \resumeItemListStart
        \resumeItem{Continued working on Jotform Tables with React, Redux and PHP.}
        \resumeItem{Solved 50+ bug tickets, working with both legacy and recent code.}
        \resumeItem{Helped my team in integrating AI functionalities to Jotform Tables.}
        \resumeItem{The contributions were taken live on a platform with 35M registered users.}
        \resumeItem{Received constant feedback from my mentor.}
      \resumeItemListEnd
      
    \resumeSubheadingRole{Frontend Developer Intern}{June 2025 -- Aug. 2025}
      \resumeItemListStart
        \resumeItem{Developed a new feature for Jotform Tables, allowing users to import external files (Excel, CSV) to their existing tables.}
        \resumeItem{Engineered frontend logic using React.}
        \resumeItem{Successfully implemented Figma design wireframes to the codebase with SCSS stylesheets.}
        \resumeItem{Utilized Redux and Redux-Saga for global state management.}
        \resumeItem{Improved soft skills by working with a team of interns, also received extensive mentorship.}
        \resumeItem{Navigated and contributed to a large-scale enterprise codebase.}
      \resumeItemListEnd

    \resumeSubheading
      {Parayuz}{Urla, Izmir, Turkey}
      {DevOps Engineer}{Sept. 2025 -- Feb. 2026}
      \resumeItemListStart
        \resumeItem{Participated in a grassroots startup environment where we developed a financial assistant application as a team of students.}
        \resumeItem{Successfully deployed the application combining three services utilizing AWS EC2, Docker Compose, and nginx.}
        \resumeItem{Created a development Docker image using Docker Compose with hot-reload functionality to speed up development.}
        \resumeItem{Set up auto-deploy functionality for certain Git branches using GitHub Actions and shell scripting.}
        \resumeItem{Utilized AWS ECS to deploy microservices with a load balancer.}
        \resumeItem{Wrote shell scripts for CI/CD pipelines.}
        \resumeItem{Helped with development work in both the frontend and the backend, using Next.js and Spring Boot respectively.}
      \resumeItemListEnd

    \resumeSubheading
      {gardostech}{Alsancak, Izmir, Turkey}
      {Junior Software Developer}{Mar. 2025 -- Sept. 2025}
      \resumeItemListStart
        \resumeItem{Worked on the company management app Krang following Agile practices.}
        \resumeItem{Built a demo app which utilizes LLMs to read and extract receipt data from a photo taken with the device camera.}
        \resumeItem{Worked with technologies like Next.js, TypeScript, and Tailwind CSS for frontend development.}
        \resumeItem{Implemented a PDF generator on the Nest.js backend to generate PDFs from HTML templates using Puppeteer and Handlebars.}
        \resumeItem{Developed a task management module integrated with other modules from scratch with isolated notifications using user groups.}
        \resumeItem{Revamped the application's notification architecture with the Nest.js backend, implemented mention notifications for the task management module.}
        \resumeItem{Created an in-app messaging module with notifications, utilizing WebSocket.}
        \resumeItem{Worked on Nest.js RESTful APIs and the Prisma database schema of the application.}
      \resumeItemListEnd

    \resumeSubheading
      {Izmir Biomedicine and Genome Center}{Balcova, Izmir, Turkey}
      {Software Developer Intern}{May 2024 -- Jan. 2025}
      \resumeItemListStart
        \resumeItem{Designed an Android application for cell counting using image processing with MATLAB, Python, and Flutter.}
        \resumeItem{Gained experience in applying software solutions to biomedicine.}
      \resumeItemListEnd

    \resumeSubheading
      {IZTECH Software Society}{Urla, Izmir, Turkey}
      {Frontend Developer}{May 2024 -- June 2025}
      \resumeItemListStart
        \resumeItem{Built a form application with Next.js and MongoDB to streamline event attendee management.}
        \resumeItem{Developed interactive projects, including a password game and a digital card app, using Next.js.}
        \resumeItem{Successfully converted a legacy project which used React and JavaScript to more modern technologies like Next.js and TypeScript.}
        \resumeItem{Collaborated with a team of 10+ developers on an educational app.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------LEADERSHIP & ACTIVITIES-----------
\section{Leadership \& Activities}
  \resumeSubHeadingListStart

    \resumeSubheading
      {IZTECH Software Society}{Urla, Izmir, Turkey}
      {Organizational Co-Leader}{Sept. 2024 -- Feb. 2025}
      \resumeItemListStart
        \resumeItem{Attracted 800+ new members during a university event, leading recruitment efforts.}
        \resumeItem{Organized large-scale events, including a welcome party with 300+ attendees and a code night with 50+ participants.}
      \resumeItemListEnd
      
    \resumeSubheadingRole{Team Member}{Oct. 2023 -- June 2025}
      \resumeItemListStart
        \resumeItem{Supported various club activities, contributing to event planning and execution.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Programming Languages}{: JavaScript, TypeScript, Java, PHP, Python, C, Shell, Dart} \\
     \textbf{Frameworks \& Libraries}{: React, Redux, Redux-Saga, Tailwind CSS, SCSS, Next.js, Nest.js, Spring Boot, Flutter} \\
     \textbf{Tools}{: Linux, Git, Docker, Docker Compose, Nginx, GitHub Actions, WebSocket} \\
     \textbf{Databases \& Cloud}{: PostgreSQL, Prisma ORM, MySQL, MongoDB, AWS (EC2, ECS), GCP, Vercel} \\
     \textbf{Languages}{: Turkish (Native), English (Professional Working Proficiency)}
    }}
 \end{itemize}

%-------------------------------------------
\end{document}